\documentclass{llncs}
\usepackage[utf8]{inputenc}

\begin{document}

% please remember the 2 pages maximum size for each workshop

\section*{Asynchronous Many-Task systems for Exascale (AMTE)}

\subsection*{Workshop Description}
The workshop, Asynchronous Many-Task Systems for Exascale (AMTE) 2023, was held on August 23rd in conjunction with the 29th International European Conference on Parallel and Distributed Computing (Euro-Par) as an in-person event in Limassol, Cyprus. The workshop explored the advantages of task-based programming on modern and future high-performance systems. It gathered developers, users, and proponents of these models and systems to share experiences, discuss how they meet the challenges posed by Exascale system architectures, and explore opportunities for increased performance, robustness, and full-system utilization.

The workshop was organized by Patrick Diehl, Steven R. Brandt, Zahra Khatami, and Parsa Amini. The keynote was given by Brad Richardson (Berkley Lab), and the invited talk was given by Jeff Hammond (NVIDIA). 

This volume of LNCS compromises selected contributions of attendees from this event. The contributed papers range from optimization of asynchronous many-task runtime systems to applications. This workshop has shown that AMTs are widely used in academia, industry, and national laboratories, and researchers are working to address some challenges posed by Excascale system architectures.


\subsection*{Steering Committee}
%Please introduce one name and affiliation per line as below.
\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
Parsa Amini & Halpern-Wight Inc., USA\\
Steven R. Brandt & Louisiana State University, USA\\
Patrick Diehl & Louisiana State University, USA\\
Zahra Khatami & NVIDIA, USA\\
\end{tabular}


%\subsection*{Program Chair}
%In case of more than one char, please introduce one name and affiliation per line as below.
%\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
%Loris Marchal & CNRS \& University of Lyon, France
%\end{tabular}

\subsection*{Program Committee}
%Please introduce one name and affiliation per line as below.
\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
Jeff Hammond & NVIDIA \\
Hartmut Kaiser & Center for Computation \& Technology at Louisiana State University, USA \\
Markus Rampp & Max Planck Computing \& Data Facility, Germany \\
Patricia Grubel & Los Alamos National Laboratory, USA \\
Bita Hasheminezhad & NASA Ames Research Center, USA \\
Pedro Valero-Lara & Oak Ridge National Laboratory, USA
\\
H. Metin Aktulga & MSU College of Engineering, USA
\\
Keita Teranishi & Sandia National Laboratories, USA
\end{tabular}

\end{document}